\publi{2022}{Observation Scheduling and Automatic Data Reduction for the Antarctic telescope, ASTEP+}
{Dransfield, G., Mekarnia, D., Triaud, A.~H.~M.~J., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022arXiv220804501D}{arXiv e-prints, arXiv:2208.04501}}

\publi{2022}{TESS discovery of a sub-Neptune orbiting a mid-M dwarf TOI-2136}
{Gan, T., Soubkiou, A., Wang, S.~X., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022MNRAS.514.4120G}{\mnras, 514, 4120}}

\publi{2022}{A study of flares in the ultra-cool regime from SPECULOOS-South}
{Murray, C.~A., Queloz, D., Gillon, M., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022MNRAS.513.2615M}{\mnras, 513, 2615}}

\publi{2022}{HST/WFC3 transmission spectroscopy of the cold rocky planet TRAPPIST-1h}
{Garcia, L., Moran, S., Rackham, B., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022BAAS...54e.050G}{\baas, 54, 102.50}}

\publi{2022}{Complex Modulation of Rapidly Rotating Young M Dwarfs: Adding Pieces to the Puzzle}
{G{\"u}nther, M.~N., Berardo, D.~A., Ducrot, E., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022AJ....163..144G}{\aj, 163, 144}}

\publi{2022}{HST/WFC3 transmission spectroscopy of the cold rocky planet TRAPPIST-1h}
{Garcia, L.~J., Moran, S.~E., Rackham, B.~V., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022arXiv220313698G}{arXiv e-prints, arXiv:2203.13698}}

\publi{2022}{PROSE: a PYTHON framework for modular astronomical images processing}
{Garcia, L.~J., Timmermans, M., Pozuelos, F.~J., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022MNRAS.509.4817G}{\mnras, 509, 4817}}

\publi{2022}{TOI-1442 b and TOI-2445 b: two ultra-short period super-Earths around M dwarfs}
{Morello, G., Parviainen, H., Murgas, F., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022arXiv220113274M}{arXiv e-prints, arXiv:2201.13274}}

\publi{2022}{TOI-2257 b: A highly eccentric long-period sub-Neptune transiting a nearby M dwarf}
{Schanche, N., Pozuelos, F.~J., G{\"u}nther, M.~N., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022A\&A...657A..45S}{\aap, 657, A45}}

\publi{2021}{A Study of Flares in the Ultra-Cool Regime from SPECULOOS-South}
{Murray, C., Queloz, D., Gillon, M., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2021AGUFM.U43B..02M}{AGU Fall Meeting Abstracts, 2021, U43B-02}}

\publi{2021}{prose: FITS images processing pipeline}
{Garcia, L.~J., Timmermans, M., Pozuelos, F.~J., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2021ascl.soft11006G}{Astrophysics Source Code Library, ascl:2111.006}}

\publi{2021}{A large sub-Neptune transiting the thick-disk M4 V TOI-2406}
{Wells, R.~D., Rackham, B.~V., Schanche, N., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2021A\&A...653A..97W}{\aap, 653, A97}}

\publi{2021}{VizieR Online Data Catalog: TOI-178 six transiting planets (Leleu+, 2021)}
{Leleu, A., Alibert, Y., Hara, N.~C., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2021yCat..36490026L}{VizieR Online Data Catalog, J/A+A/649/A26}}

\publi{2021}{Six transiting planets and a chain of Laplace resonances in TOI-178}
{Leleu, A., Alibert, Y., Hara, N.~C., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2021A\&A...649A..26L}{\aap, 649, A26}}

\publi{2021}{SPECULOOS: Ultracool dwarf transit survey. Target list and strategy}
{Sebastian, D., Gillon, M., Ducrot, E., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2021A\&A...645A.100S}{\aap, 645, A100}}

\publi{2020}{Development of the SPECULOOS exoplanet search project}
{Sebastian, D., Pedersen, P.~P., Murray, C.~A., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2020SPIE11445E..21S}{\procspie, 11445, 1144521}}

\publi{2020}{VizieR Online Data Catalog: SPECULOOS. Ultracool dwarf transit survey (Sebastian+, 2021)}
{Sebastian, D., Gillon, M., Ducrot, E., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2020yCat..36450100S}{VizieR Online Data Catalog, J/A+A/645/A100}}

\publi{2020}{{\ensuremath{\pi}} Earth: A 3.14 day Earth-sized Planet from K2's Kitchen Served Warm by the SPECULOOS Team}
{Niraula, P., Wit, J. de ., Rackham, B.~V., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2020AJ....160..172N}{\aj, 160, 172}}

\publi{2020}{A super-Earth and a sub-Neptune orbiting the bright, quiet M3 dwarf TOI-1266}
{Demory, B.-O., Pozuelos, F.~J., G{\'o}mez Maqueo Chew, Y., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2020A\&A...642A..49D}{\aap, 642, A49}}

\publi{2020}{The SPECULOOS Project: New targets to hunt planets of Ultra-cool dwarfs.}
{Sebastian, D., Gillon, M., Ducrot, E., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2020EPSC...14..337S}{European Planetary Science Congress, EPSC2020-337}}

\publi{2020}{GJ 273: on the formation, dynamical evolution, and habitability of a planetary system hosted by an M dwarf at 3.75 parsec}
{Pozuelos, F.~J., Su{\'a}rez, J.~C., de El{\'\i}a, G.~C., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2020A\&A...641A..23P}{\aap, 641, A23}}

\publi{2020}{Complex Modulation of Rapidly Rotating Young M Dwarfs: Adding Pieces to the Puzzle}
{G{\"u}nther, M.~N., Berardo, D.~A., Ducrot, E., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2020arXiv200811681G}{arXiv e-prints, arXiv:2008.11681}}

\publi{2020}{Photometry and performance of SPECULOOS-South}
{Murray, C.~A., Delrez, L., Pedersen, P.~P., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2020MNRAS.495.2446M}{\mnras, 495, 2446}}

\publi{2018}{Validation of a CCD cosmic ray event simulator against Gaia in-orbit data}
{Garcia, L., Prod'homme, T., Lucsanyi, D., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2018SPIE10709E..19G}{\procspie, 10709, 1070919}}

