\publi{2023}{An M dwarf accompanied by a close-in giant orbiter with SPECULOOS}
{Triaud, A.~H.~M.~J., Dransfield, G., Kagetani, T., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2023MNRAS.525L..98T}{\mnras, 525, L98}}

\publi{2023}{TESS discovery of a super-Earth orbiting the M-dwarf star TOI-1680}
{Ghachoui, M., Soubkiou, A., Wells, R.~D., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2023A\&A...677A..31G}{\aap, 677, A31}}

\publi{2023}{WASP-193b: An extremely low-density super-Neptune}
{Barkaoui, K., Pozuelos, F.~J., Hellier, C., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2023arXiv230708350B}{arXiv e-prints, arXiv:2307.08350}}

\publi{2023}{TOI-1442 b and TOI-2445 b: Two potentially rocky ultra-short period planets around M dwarfs}
{Morello, G., Parviainen, H., Murgas, F., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2023A\&A...673A..32M}{\aap, 673, A32}}

\publi{2023}{A super-Earth and a mini-Neptune near the 2:1 MMR straddling the radius valley around the nearby mid-M dwarf TOI-2096}
{Pozuelos, F.~J., Timmermans, M., Rackham, B.~V., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2023A\&A...672A..70P}{\aap, 672, A70}}

\publi{2023}{Precise near-infrared photometry, accounting for precipitable water vapour at SPECULOOS Southern Observatory}
{Pedersen, P.~P., Murray, C.~A., Queloz, D., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2023MNRAS.518.2661P}{\mnras, 518, 2661}}

\publi{2022}{Two temperate super-Earths transiting a nearby late-type M dwarf}
{Delrez, L., Murray, C.~A., Pozuelos, F.~J., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022A\&A...667A..59D}{\aap, 667, A59}}

\publi{2022}{SPECULOOS Northern Observatory: Searching for Red Worlds in the Northern Skies}
{Burdanov, A.~Y., de Wit, J., Gillon, M., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022PASP..134j5001B}{\pasp, 134, 105001}}

\publi{2022}{TESS discovery of a sub-Neptune orbiting a mid-M dwarf TOI-2136}
{Gan, T., Soubkiou, A., Wang, S.~X., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022MNRAS.514.4120G}{\mnras, 514, 4120}}

\publi{2022}{Observation scheduling and automatic data reduction for the Antarctic Telescope, ASTEP+}
{Dransfield, G., M{\'e}karnia, D., Triaud, A.~H.~M.~J., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022SPIE12186E..1FD}{\procspie, 12186, 121861F}}

\publi{2022}{A study of flares in the ultra-cool regime from SPECULOOS-South}
{Murray, C.~A., Queloz, D., Gillon, M., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022MNRAS.513.2615M}{\mnras, 513, 2615}}

\publi{2022}{Complex Modulation of Rapidly Rotating Young M Dwarfs: Adding Pieces to the Puzzle}
{G{\"u}nther, M.~N., Berardo, D.~A., Ducrot, E., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022AJ....163..144G}{\aj, 163, 144}}

\publi{2022}{TOI-1442 b and TOI-2445 b: two ultra-short period super-Earths around M dwarfs}
{Morello, G., Parviainen, H., Murgas, F., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022arXiv220113274M}{arXiv e-prints, arXiv:2201.13274}}

\publi{2022}{TOI-2257 b: A highly eccentric long-period sub-Neptune transiting a nearby M dwarf}
{Schanche, N., Pozuelos, F.~J., G{\"u}nther, M.~N., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2022A\&A...657A..45S}{\aap, 657, A45}}

\publi{2021}{A large sub-Neptune transiting the thick-disk M4 V TOI-2406}
{Wells, R.~D., Rackham, B.~V., Schanche, N., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2021A\&A...653A..97W}{\aap, 653, A97}}

\publi{2021}{Six transiting planets and a chain of Laplace resonances in TOI-178}
{Leleu, A., Alibert, Y., Hara, N.~C., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2021A\&A...649A..26L}{\aap, 649, A26}}

\publi{2021}{SPECULOOS: Ultracool dwarf transit survey. Target list and strategy}
{Sebastian, D., Gillon, M., Ducrot, E., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2021A\&A...645A.100S}{\aap, 645, A100}}

\publi{2020}{Development of the SPECULOOS exoplanet search project}
{Sebastian, D., Pedersen, P.~P., Murray, C.~A., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2020SPIE11445E..21S}{\procspie, 11445, 1144521}}

\publi{2020}{{\ensuremath{\pi}} Earth: A 3.14 day Earth-sized Planet from K2's Kitchen Served Warm by the SPECULOOS Team}
{Niraula, P., Wit, J. de ., Rackham, B.~V., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2020AJ....160..172N}{\aj, 160, 172}}

\publi{2020}{A super-Earth and a sub-Neptune orbiting the bright, quiet M3 dwarf TOI-1266}
{Demory, B.-O., Pozuelos, F.~J., G{\'o}mez Maqueo Chew, Y., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2020A\&A...642A..49D}{\aap, 642, A49}}

\publi{2020}{GJ 273: on the formation, dynamical evolution, and habitability of a planetary system hosted by an M dwarf at 3.75 parsec}
{Pozuelos, F.~J., Su{\'a}rez, J.~C., de El{\'\i}a, G.~C., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2020A\&A...641A..23P}{\aap, 641, A23}}

\publi{2020}{Photometry and performance of SPECULOOS-South}
{Murray, C.~A., Delrez, L., Pedersen, P.~P., et al. (including Garcia L.~J.)}
{\href{https://ui.adsabs.harvard.edu/abs/2020MNRAS.495.2446M}{\mnras, 495, 2446}}